Figures

### 2018-03-21 scripts/analysis.Rmd
crop conny metric key
include iws diagram, reorder figs

@@

```{r fig.cap="Connectivity metric box"}
knitr::include_graphics("../figures/conny_metric_key.pdf")
```

>>>>

```{r fig.cap="Watershed diagram", echo=FALSE}
knitr::include_graphics("../figures/iws_nws.pdf")
```

```{r fig.cap="Connectivity metric box", echo=FALSE}
knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
```

@@
